Report - Latest Rodent Data

### 2018-04-13 index.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance("repo", level='treatment', length="longterm") %>%
  filter(treatment=="control")
obs_data$total = rowSums(select(obs_data, -c(period, treatment)))
new_moons = read.csv(text = RCurl::getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance("repo", clean=FALSE, level='treatment', length="longterm") %>%
  filter(treatment=="control")
obs_data$total = rowSums(select(obs_data, -c(period, treatment)))
new_moons = read.csv(text = RCurl::getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))

### 2018-04-13 report.Rmd

# get most recent rodent data
rodents = abundance("repo", shape='flat', level='treatment')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period, treatment=='control')

@@

# get most recent rodent data
rodents = abundance("repo", shape='flat')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period)

>>>>

# get most recent rodent data
rodents = abundance("repo", clean=FALSE, shape='flat', level='treatment', length='longterm')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period, treatment=='control')

@@

# get most recent rodent data
rodents = abundance("repo", clean=FALSE, shape='flat')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period)
